paper_data

### 2023-08-23 paper_codes.Rmd
final commit

## Libraries

@@

Netherlands boundary shapefile

@@

Data for vegetation plots and abiotic measurements data

@@

Data for Netherlands grid

@@

## Experiments: training and validation

@@

Combine and export the results of fitting all models to data:

@@

>>>>

## Libraries
For INLA, see: https://www.r-inla.org/download-install

@@

Netherlands boundary shapefile
Coordinates are in EPSG:28992, the Projected coordinate system for Netherlands. These coordinates are calculated from the center of the Netherlands in meters. For simplicity, we convert them to kilometers below.

@@

Data for vegetation plots and abiotic measurements data
Coordinates are in EPSG:28992, the Projected coordinate system for Netherlands.

@@

Data for Netherlands grid
Coordinates are in EPSG:28992, the Projected coordinate system for Netherlands.

@@

## Experiments: training and validation
It is also possible to download the results from https://zenodo.org/record/8261504
In that case, place the downloaded files in the subfolder `data_paper/` and go to the `Results: import file` section below to import the results and create the plots.

@@

Combine and export the results of fitting all models to data: 
It is also possible to skip this cell and download the results from https://zenodo.org/record/8261504
Place the data in the subfolder `data_paper/` and run the code below this cell to create the plots.

@@

## Results: import file

### 2023-08-23 paper_data.Rmd
final commit

## Original LMF data set to LMF subset
Here as well as in the modelling code, all coordinates are in EPSG:28992 Projected coordinate system for Netherlands.

@@

```{r}
NL <- st_read("data_paper/NL.shp")$geometry
NL <- (NL - matrix(data=c(155000, 463000), ncol=2)) * matrix(data=c(1/1000, 1/1000), ncol=2)
```

>>>>

## Original LMF data set to LMF subset
Fetch Netherlands boundaries from RIVM GIS server. Here as well as in the modelling code, all coordinates are in EPSG:28992 Projected coordinate system for Netherlands.

```{r}
conn <- dbConnect(PostgreSQL(), dbname="geodata", user = "", password="", host = "geodatabase.rivm.nl")
NL <- st_read(conn, query = "SELECT * FROM nl.adm_wijkbuurt_2022_gen;") %>%
  filter(indeling == 'gemeente') %>% st_union()
st_write(NL, "data_paper/NL.shp", append=F)
```

@@

```{r}
NL <- (NL - matrix(data=c(155000, 463000), ncol=2)) * matrix(data=c(1/1000, 1/1000), ncol=2)
```
